Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Add top-level spec to Hspec example
Enhance "Integrating multiple test suites"

\begin{quote}
\small
\begin{verbatim}
import Test.Hspec.Monadic
main :: IO ()
main = spec $ do
  describe "reverse" $ do
    it "reverses a list" $
      assertEqual "" [3, 2, 1] (reverse [1, 2, 3])

@@

A driver for Hspec looks like so:

\begin{quote}
\small
\begin{verbatim}
-- file Spec.hs
import Test.Hspec.Monadic
main = hspec spec
\end{verbatim}
\end{quote}

>>>>

main :: IO ()
main = hspec spec

spec :: Spec
spec = do
  describe "reverse" $ do
    it "reverses a list" $
      assertEqual "" [3, 2, 1] (reverse [1, 2, 3])

@@

As discussed in \ref{sec:solution-discovery}, we can use {\tt
hspec-discover} to automatically generate a test driver for Hspec:

\begin{quote}
\small
\begin{verbatim}
-- file Spec.hs
{-# OPTIONS_GHC -F -pgmF hspec-discover #-}
\end{verbatim}
\end{quote}

\noindent A corresponding Cabal test suite section looks like this:
